Stable Hot Spot Analysis (Draft)

### 2017-06-16 paper-main.tex
Added degress in WGS84 after: https://www.deine-berge.de/Rechner/Koordinaten/Dezimal/40.769239,-73.948286

We evaluate our data on the New York city yellow cab data set \footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}. This data set includes all taxi drives from the yellow cabs in New York City, from location, to passengers and many more informations. In this study, we compare the total pickups over January from 2016 in the Manhattan area. The borders of the rasters are (40.699607, -74.020265) and (40.769239, -73.948286). By using this data set, we reduce the computational effort while still being able to show the applicability on real world data and problems.
\subsection{Treatments}

>>>>

We evaluate our data on the New York city yellow cab data set 
\footnote{$http://www.nyc.gov/html/tlc/html/about/trip\_record\_data.shtml$}. 
This data set includes all taxi drives from the yellow cabs in New York City, 
from location, to passengers and many more informations. In this study, we compare the 
total pickups over January from 2016 in the Manhattan area. 
The borders of the rasters are (40.699607 \textdegree  (N), -74.020265 \textdegree  (E)) and (40.769239, -73.948286).
By using this data set, we reduce the computational effort while still 
being able to show the applicability on real world data and problems.
\subsection{Treatments}
